DOpElib:\\ Differential Equations and Optimization Environment

### 2013-12-10 Examples/OPT/InstatPDE/Example1/content.tex
Update Doku

The following new things differ from the PDE-Eamples and the optimization examples with stationary 
PDEs:\\[2mm]
In the file \texttt{main.cc} the SpaceTimeHandler now gets an additional argument.
In this case \texttt{DOpEtypes::initial} which specifies that the control is entering in the 
initial value.\\[2mm]
In the file \texttt{localpde.h} we now have to specify the Methods \texttt{Init\underline{ }ElementRhs}
and \texttt{Init\underline{ }ElementRhs\underline{ }Q}. They need to be adapted, since usualy the InitialValue for the 
PDE is auto generated from a deal.ii function in the ProblemContainer. This Value is set in the 
\texttt{Init\underline{ }ElementRhs} hence we need to change this function to use the control instead. 
Correspondingly we need to implement the first derivative of this with respect to the control. 
--We don't need the second derivative since it is zero anyways.--\\[2mm]

>>>>

\subsubsection{Program description}
The following new things differ from the PDE-Eamples and the optimization examples with stationary 
PDEs:\\[2mm]
\twick{
First, we need to introduce a reasonable dual time-stepping scheme in the main
file since we have to
compute 
the adjoint equation backward in time. 
Next,} in the file \texttt{main.cc} the SpaceTimeHandler now gets an additional argument.
In this case \texttt{DOpEtypes::initial} which specifies that the control is entering in the 
initial value.\\[2mm]
In the file \texttt{localpde.h} we now have to specify the Methods \texttt{Init\underline{ }ElementRhs}
and \texttt{Init\underline{ }ElementRhs\underline{ }Q}. They need to be adapted, since usualy the InitialValue for the 
PDE is auto generated from a deal.ii function in the ProblemContainer. This Value is set in the 
\texttt{Init\underline{ }ElementRhs} hence we need to change this function to use the control instead. 
Correspondingly we need to implement the first derivative of this with respect to the control. 
--We don't need the second derivative since it is zero anyways.--\\[2mm]
